---
title: "Final Project Codebook"
subtitle: "Data Science II (STAT 301-2)"
author: "Sammy Mustafa"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: "tango"
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```
<br>

## Data Source
```{r, message = FALSE}
shrooms <- read_csv("data/mushrooms.csv")
```
This data set documents various properties of mushrooms including its class, cap_shape, cap_surface, bruises, odor, gill_size, population, habitat, and other properties of its parts (as shown in the image below) of over 8,000 different mushroom samples.
<br><br>


## Data Citation: 

Kaggle, 2019, "Mushroom Classification with ANN," https://www.kaggle.com/gulsahdemiryurek/mushroom-classification-with-ann/data

<br><br>


### Variables
All the variables within the data set are categorical and depict a physical property of the mushroom.


**class**: if mushroom is edible or poisonous
<br>
**cap_shape**: shape of mushroom cap
<br>
**cap_surface**: surface of mushroom cap
<br>
**cap-color**: color of mushroom cap
<br>
**bruises**: if there are bruises or no bruises on the mushroom
<br>
**odor**: the odor of the mushroom
<br>
**gill_attachment**: how the mushroom's gills are attached
<br>
**gill_spacing**: how the mushroom's gills are spaced
<br>
**gill_size**: the size of the mushroom's gills
<br>
**gill_color**: the color of the mushroom's gills
<br>
**stalk_shape**: the shape of the mushroom's stalk
<br>
**stalk_root**: the root of the mushroom's stalk
<br>
**stalk_surface_above_ring**: the type of surface on the stalk above the mushroom's ring
<br>
**stalk_surface_below_ring**: the type of surface on the stalk below the mushroom's ring
<br>
**stalk_color_above_ring**: the color of the stalk above the mushroom's ring
<br>
**stalk_color_below_ring**: the color of the stalk below the mushroom's ring
<br>
**veil_type**: the type of mushroom veil
<br>
**veil_color**: the color of the mushroom's veil
<br>
**ring_number**: the number of rings the mushroom has
<br>
**ring_type**: the type of ring the mushroom has
<br>
**spore_print_color**: the color of the spores on the mushroom
<br>
**population**: how the mushroom grows
<br>
**habitat**: the habitat in which the mushroom grows
<br>
